\textcolor{sage}{Does Hospital Leadership Matter? \newline Evidence from Pay-for-Performance}

### 2025-10-30 Slides/ASHE2025.tex
Updates from Overleaf

% Title Slide
\begin{frame}[plain]
% Background image
\begin{tikzpicture}[remember picture,overlay]
    \node
[
    above=0.5cm,
    align=center,
    fill=lightcyan,
    rounded corners,
    inner xsep=15pt,
    inner ysep=10pt, 
    minimum width=0.9\textwidth,
    text width=0.6\textwidth
] (title) at (current page.center)
{
    \LARGE Does Hospital Leadership Matter?  \\[5pt]
    \large Evidence from Pay-for-Performance
};
% Author 
\node[below=1cm] (author) at (title.south){\large Hanna Glenn, Emory University};
% Date
\node[below=0.25cm] (date) at (author.south){\today};
\end{tikzpicture}

@@

@@

\begin{frame}{Gaps in Literature}
    \large
    \begin{enumerate}
        \item Findings are limited to large, publicly traded firms

        \begin{itemize}
            \item \normalsize Different objectives/incentives in other types of firms (nonprofits)
        \end{itemize}

        \item Unclear whether leadership matters when policies change incentives
    \end{enumerate}
\end{frame}

@@

\vspace{5mm} \large \pause

\begin{enumerate}
    \item \textbf{Hospital care makes up a third of health care spending} \scriptsize (\cite{cms2024nhe}) \normalsize

@@

    \begin{itemize}
        \item \normalsize Nonprofits drive the hospital industry \scriptsize (\cite{ASPE_2023}) \normalsize
    \end{itemize}

    \item \large \textbf{Policies often aim to improve the value of health care delivery}

    \begin{wideitemize}
        \item \normalsize Unclear how leaders interact with this goal
    \end{wideitemize}

@@

\begin{frame}{Research Question}
    \centering
    \Large
    Do executives with clinical training

@@

    affect response to pay-for-performance incentives

@@

\begin{frame}{Why Clinical Training?}

@@

\textbf{Do physicians make good firm leaders?}

\begin{wideitemize}
    \item Relevant expertise \scriptsize (\cite{Stajduhar_2023}, \cite{Ahmed_2022}) \large

    \item Lack of business training \scriptsize (\cite{HarvardBusinessReview2018})
\end{wideitemize}

\vspace{12mm}

\textbf{Potentially correlated with how the leader values quality versus profit}
\end{frame}

\begin{frame}{Pay-for-Performance Incentives}
    \large
    \begin{block}{\Large Main Takeaway:}
        \large 
        \centering
        \vspace{1mm}
        Hospitals now have financial incentives to improve quality

        \vspace{1mm}
    \end{block}

    \vspace{6mm}

    \textbf{Quality: 30-day readmissions \& 30-day mortality}

    Hospital Readmissions Reduction Program
    \begin{itemize}
        \item Penalized high readmissions
        \item Pneumonia, Heart Attack (AMI), Heart Failure
    \end{itemize}

    Hospital Value-Based Purchasing Program
    \begin{itemize}
        \item Score metric determines rewards
        \item Rewards high metric
    \end{itemize}
\end{frame}

\begin{frame}{Preview of Main Findings}

\textbf{Non-clinical executive teams respond more to financial incentives on quality}

\begin{wideitemize}
    \item Through readmission rates
    \item Non-clinical executive teams behave like profit-driven hospitals
\end{wideitemize}
\end{frame}

\begin{frame}{Contribution}
\large
    \textbf{Hospital Executives/Board of Directors}

    \begin{wideitemize}
        \item \normalsize Physician board members $\implies$ lower public donations \scriptsize (\cite{brickley2010board}) \normalsize
        \item No correlation b/w CEOs and hospital productivity in England \scriptsize (\cite{janke2019impact})\normalsize
        \item Public hospitals in Chile improved when older physicians left CEO \scriptsize (\cite{otero2022managers}) \normalsize
    \end{wideitemize}

    \vspace{5mm}\pause

    \textbf{Hospital Response to Pay-for-Performance}

    \begin{wideitemize}
        \item \normalsize Hospitals decreased readmissions \scriptsize (\cite{gupta2021impacts}) \normalsize
        \item Market concentration and systems affect response \scriptsize (\cite{kunz2024assessing}) \normalsize
        \item Rewards had little impact on quality \scriptsize (\cite{norton2018moneyball}; \cite{friedson2019so})
    \end{wideitemize}
\end{frame}

\begin{frame}{Rest of Talk}

    Setting and Data Collection

    About Executive Teams

    Theoretical Motivation

    Effect of Clinical Leadership

    Comparison to For-Profits

    Signaling vs. Managing
\end{frame}

\begin{transitionframe}
\centering \LARGE
    \textcolor{black}{Setting and Data Collection}
\end{transitionframe}

\begin{frame}{About the Executives}\label{nonprofithospexec}

\large
\textbf{What do they do?}

\begin{wideitemize}
    \item Board of directors selects executives
    \item Executives handle the day-to-day operations of the hospital 
    \item Quality often improved from the top down \scriptsize (\cite{silow2011reducing})
\end{wideitemize}

\vspace{4mm} \pause

\textbf{Executive teams}

\begin{wideitemize}
    \item Lot of variation in team organization
    \item CEO and CFO
    \item I focus on the team as a whole instead of specific executive roles
\end{wideitemize}

\hyperlink{executivejob}{\beamergotobutton{executive job}}

\begin{frame}{Data Collection Process}
\begin{center}
\begin{tikzpicture}[
    node distance=3.1cm and 1.8cm,
    every node/.style={align=center, font=\normalsize},
    process/.style={rectangle, draw, rounded corners, text centered, minimum width=2.5cm, minimum height=2cm, fill=purple!30},
    output/.style={rectangle, draw, text centered, minimum width=2.7cm, minimum height=2.5cm, fill=purple},
    extract/.style={rectangle, draw, rounded corners, text centered, minimum width=2.5cm, minimum height=2cm, fill=sage!30},
    arrow/.style={thick, ->, >=stealth}
]

% Nodes
\node (step1) [process] {Hospital \\EINs};\pause
\node (step2) [process, right of=step1] {Download \\PDFs};
\draw[arrow] (step1) -- (step2); \pause
\node (step3) [process, right of=step2] {Extract\\text};
\draw[arrow] (step2) -- (step3); 
% New green box below step3
\node (extract) [extract, below of=step3, yshift=0.5cm] {Optical\\Character\\Recognition}; 
\draw[arrow] (extract) -- (step3);\pause
\node (step4) [process, right of=step3] {String\\cleaning\\algorithms};
\draw[arrow] (step3) -- (step4); \pause
\node (output) [output, right of=step4, text=white] {Executive\\Name\\Position\\Title};
\draw[arrow] (step4) -- (output);
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{Merge to Other Data}

\large
    \textbf{Hospital:}

    \vspace{2mm}
    \begin{wideitemize}
        \item AHA
        \item Hospital Compare
        \item CMS Case Mix Index
        \item Health Care Cost Report Information System (HCRIS)
    \end{wideitemize}

    \vspace{7mm}

@@

    \begin{itemize}
        \item Manually match physician executives to NPPES NPI number
    \end{itemize}
\end{frame}

@@

\begin{transitionframe}
\centering \LARGE
    \textcolor{black}{Descriptive Statistics}
\end{transitionframe}

\begin{frame}{Executive Teams}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
\toprule
 & Ever & Always & Never\\
  & Clinical Exec & Clinical Exec & Clinical Exec\\
\midrule
\addlinespace[0.3em]
Number Executives & 4.82 & 5.19 & 2.86\\
Fraction Clinical Execs & 0.20 & 0.26 & 0.00\\
Fraction Int. Medicine Execs & 0.06 & 0.08 & 0.00\\
Has a CMO & 0.55 & 0.52 & 0.07\\
Has Clinical CEO & 0.25 & 0.10 & 0.00\\
\addlinespace[0.6em]
Num. Hospitals & 452 & 62 & 385\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

\begin{frame}{Hospital Statistics}\label{sumstats}
\vspace{-3mm}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
 & Ever & Always & Never\\
  & Clinical Exec &Clinical Exec &Clinical Exec\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
\hspace{1em}Academic Med. Center & 0.41 & 0.51 & 0.20\\
\hspace{1em}Number Beds & 227 & 218 & 102\\
\hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
\hspace{1em}System Affiliated & 0.57 & 0.56 & 0.42\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
\hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.77 & 0.59\\
\hspace{1em}Penalized for one condition & 0.19 & 0.25 & 0.13\\
\hspace{1em}Penalized for AMI + HF & 0.07 & 0.05 & 0.03\\
\hspace{1em}Penalized for AMI + Pneumonia & 0.02 & 0.02 & 0.02\\
\hspace{1em}Penalized for HF + Pneumonia & 0.41 & 0.40 & 0.33\\
\hspace{1em}Penalized for All Conditions & 0.31 & 0.31 & 0.20\\
\bottomrule
\end{tabular}
\end{table}
\hyperlink{forprofitstats}{\beamergotobutton{for-profit stats}}
\end{frame}

@@

\section{Theoretical Framework}

\begin{transitionframe}
\centering \LARGE
    \textcolor{black}{Theoretical Framework}
\end{transitionframe}

\begin{frame}{Hospital Objectives: Profit versus Patient Welfare}
    \Large
    \centering
    \begin{equation*}
        \max_{\theta}\hspace{2mm} \alpha\pi(\theta) + (1-\alpha)u(\theta)
    \end{equation*}
\end{frame}

\begin{frame}[noframenumbering]{Hospital Objectives: Profit versus Patient Welfare} \Large
    \begin{equation*}
\max_{\theta}\hspace{2mm}\alpha
\tikz[baseline]{
    \node[draw=sage,rounded corners,anchor=base] (m1)
    {$\pi(\theta)$};
    \node[above of=m1, text=sage, yshift=5mm] (l1) {profit};
    \draw[-,sage] (l1) -- (m1);
}
+ (1-\alpha)\hspace{-11mm}
\tikz[baseline]{
    \node[draw=sage,rounded corners,anchor=base] (m2)
    {$u(\theta)$};
    \node[above of=m2, text=sage, yshift=5mm] (l2) {patient welfare};
    \draw[-,sage] (l2) -- (m2);
}
\end{equation*}
\end{frame}

\begin{frame}[noframenumbering]{Hospital Objectives: Profit versus Patient Welfare} \Large
    \begin{equation*}
\max_{\theta}\hspace{2mm}\alpha\pi(\hspace{-5mm}
\tikz[baseline]{
    \node[draw=purple,rounded corners,anchor=base] (m1)
    {$\theta$};
    \node[above of=m1, text=purple, yshift=5mm] (l1) {quality};
    \draw[-,purple] (l1) -- (m1);
}
\hspace{-5mm}) + (1-\alpha)u(\hspace{-5mm}
\tikz[baseline]{
    \node[draw=purple,rounded corners,anchor=base] (m2)
    {$\theta$};
    \node[above of=m2, text=purple, yshift=5mm] (l2) {quality};
    \draw[-,purple] (l2) -- (m2);
}
\hspace{-5mm})
\end{equation*}
\end{frame}

\begin{frame}[noframenumbering]{Hospital Objectives: Profit versus Patient Welfare} \Large
    \begin{equation*}
\max_{\theta}\hspace{-4mm}
\tikz[baseline]{
    \node[draw=earthyellow,rounded corners,anchor=base] (m1)
    {$\alpha$};
    \node[above of=m1, text=earthyellow, yshift=5mm] (l1) {weight on\\profit};
    \draw[-,earthyellow] (l1) -- (m1);
}
\hspace{-8mm}\pi(\theta) + \hspace{-7mm}
\tikz[baseline]{
    \node[draw=earthyellow,rounded corners,anchor=base] (m2)
    {$(1-\alpha)$};
    \node[above of=m2, text=earthyellow, yshift=5mm] (l2) {weight on\\patient welfare};
    \draw[-,earthyellow] (l2) -- (m2);
}
\hspace{-7mm}u(\theta)
\end{equation*}
\end{frame}

\begin{frame}{Choice of Quality}\label{choiceofquality}

\vspace{9mm}

\Large

    \begin{columns}
    \begin{column}{0.5\textwidth}
    \begin{center}
        \underline{Fee-for-Service}

            $\pi$ $\downarrow$ in $\theta$
    \end{center}
    \end{column}
    \begin{column}{0.5\textwidth}  %%<--- here
    \begin{center}
        \underline{Pay-for-Performance}

            $\pi$ $\uparrow$ in $\theta$
    \end{center}
    \end{column}
\end{columns}

\begin{block}{\Large Fee-for-service to Pay-for-performance}
    \centering
    \vspace{3mm}
    Higher $\alpha$ $\implies$ larger response

    \vspace{3mm}
\end{block}

\hyperlink{choiceofqualityapp}{\beamergotobutton{more details}}
\end{frame}

\begin{frame}{Informing the Empirical Analysis}

\large
    \begin{enumerate}
        \item If clinicians affect $\alpha$, they affect quality change after P4P

        \vspace{8mm}\pause
        \item If non-clinicians have higher $\alpha$, they act more like for-profits

        \vspace{8mm}\pause
        \item Mechanism could be revealing objectives or changing objectives
    \end{enumerate}
\end{frame}

@@

    Different methods:
    \begin{itemize}
        \item No weights
        \item \textbf{``Synthetic DiD" type weights} 
        \item Coarsened exact matching 
    \end{itemize}
\end{frame}

\begin{frame}{Identification Assumptions}

\large
\begin{wideitemize}
    \item Parallel trends
    \item No other 2012 event correlated with executive team and outcomes
    \item No hospital characteristics perfectly correlated with executive team
    \item No anticipation of incentive changes
    \item Stability in clinical executives not correlated with incentive change
\end{wideitemize}
\end{frame}

\begin{frame}{Average Team Changes Over Time}
\centering 
    \includegraphics[width=.8\textwidth]{Objects/change_means.pdf}
\end{frame}

@@

\begin{frame}{Estimation}
\large
    \textbf{Compare both nonprofit leadership team types to the response of for-profits:}

@@

    Comparison group:
    \begin{itemize}
        \item nonprofit clinical; nonprofit non-clinical
    \end{itemize}

@@

\begin{frame}{Mortality Rate}
    \begin{columns}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_md_synth_graph.pdf}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_nomd_synth_graph.pdf}
    \end{columns}
\end{frame}

\section{Signaling vs. Managing}

\begin{transitionframe}
\centering \LARGE
    \textcolor{black}{Signaling vs. Managing}
\end{transitionframe}

\begin{frame}{Hypotheses}

\large
    \textbf{Clinical leaders represent underlying objectives ($\alpha$)}

@@

    \begin{wideitemize}
        \item Timing of the clinical leader doesn't matter 
    \end{wideitemize}

    \vspace{15mm}

    \textbf{Clinical leaders effectively change objectives ($\alpha$)}

    \begin{wideitemize}
        \item Timing of the clinical leader does matter
    \end{wideitemize}
\end{frame}

\begin{frame}{Estimation}
\large
    \begin{figure}[ht!]
\begin{center}

 \begin{tabular}{| m{15em} |}
 \hline \vspace{1mm}
 \textbf{Signaling:}\\ [0.5ex]
 \hline\hline 
 \vspace{2mm}
 Treat Group:  \hspace{15mm} Never MD \\
 \vspace{2mm}
 Comparison Group: \hspace{3mm} Ever MD  \\
 [1ex]
 \hline
 \end{tabular}
\hfil   %<---
 \begin{tabular}{|m{18em}|}
 \hline \vspace{1mm}
 \textbf{Managing:}\\ [0.5ex]
 \hline\hline
 \vspace{2mm}
 Treat Group: \hspace{11mm} MD in 2012 \\
 \vspace{2mm}
 Comparison Group:  MD not in 2012  \\
 [1ex]
 \hline
 \end{tabular}

\begin{frame}{Results}
    \begin{table}[ht!]
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\underline{Weighted Avg. Readmission Rate}} & \multicolumn{2}{c}{\underline{Weighted Avg. Mortality Rate}} \\
 & (1) & (2) & (3) & (4)\\
\midrule
Signaling Effect & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
Managing Effect &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
Observations & 3,005 & 1,595 & 3,005 & 1,595\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@

@@

    \textbf{Implications}
    \begin{itemize}
        \item Not all nonprofits have the same objectives
        \item More clinicians in leadership could shift objectives towards quality
    \end{itemize}

    \textbf{Future Work}

    \begin{itemize}
        \item Effects of mandated gender and racial diversity on hospital behavior
        \item Networks of executives over time 
        \item Are leaders correlated with hospital fraudulent behavior?
    \end{itemize}
\end{frame}

\begin{transitionframe}
\centering 
%\includegraphics[width=.2\textwidth]{Graphics/HannaGlenn_headshot.jpg}

\Large
    Thank you!

    \vspace{15mm}

    \textcolor{black}{\faEnvelope \hspace{2mm} hanna.glenn@emory.edu}

    \textcolor{black}{\faTwitter \hspace{2mm} @hannalynnglenn}
\end{transitionframe}

@@

\begin{wideitemize}
    \item Improving care transition from inpatient to outpatient
    \item Patient education
    \item Improve care coordination
    \item Follow-up appointments
\end{wideitemize}

@@

@@

\begin{frame}{Raw Outcomes with For-Profit}\label{fp_outcomes}
\begin{center}
    \includegraphics[width=\textwidth]{}
\end{center}
    \btVFill
    \hyperlink{outcomes}{\beamerreturnbutton{outcomes graph}}
\end{frame}

@@

>>>>

% Title Slide
\begin{frame}[plain]
% Background image
\begin{tikzpicture}[remember picture,overlay]
    \node
[
    above=0.5cm,
    align=center,
    fill=lightcyan,
    rounded corners,
    inner xsep=15pt,
    inner ysep=10pt, 
    minimum width=0.9\textwidth,
    text width=0.6\textwidth
] (title) at (current page.center)
{
    \LARGE Does Hospital Leadership Matter?  \\[5pt]
    \large Evidence from Pay-for-Performance
};
% Author 
\node[below=1cm] (author) at (title.south){\large Hanna Glenn};
% Affiliation
\node[below=0.15cm] (affiliation) at (author.south){\large The University of Queensland};
% Date
\node[below=0.5cm] (date) at (affiliation.south){\today};
\end{tikzpicture}

@@

\begin{frame}{Leadership Characteristics and Firm Behavior/Performance}
\large
\begin{columns}[T]
    \begin{column}{0.45\textwidth}
    \textbf{Characteristics:}
        \begin{itemize}
            \item \tikz[baseline]{\node[anchor=base] (L1) {Gender};}
            \item \tikz[baseline]{\node[anchor=base] (L2) {Experience};}
            \item \tikz[baseline]{\node[anchor=base] (L3) {Age};}
        \end{itemize}
    \end{column}
    \begin{column}{0.45\textwidth}
    \textbf{Firm Outcomes:}
        \begin{itemize}
            \item \tikz[baseline]{\node[anchor=base] (R1) {Value};}
            \item \tikz[baseline]{\node[anchor=base] (R2) {Employees};}
            \item \tikz[baseline]{\node[anchor=base] (R3) {M\&A};}
            \item \tikz[baseline]{\node[anchor=base] (R4) {Leader Salaries};}
        \end{itemize}
    \end{column}
\end{columns}

% Now draw arrows between the nodes
\begin{tikzpicture}[overlay, remember picture]
    \draw[->, thick, shorten >=15pt] (L1.east) to [out=0, in=180] (R1.west);
    \draw[->, thick, shorten >=15pt] (L1.east) to [out=0, in=180] (R2.west);
    \draw[->, thick, shorten >=15pt] (L2.east) to [out=0, in=180] (R3.west);
    \draw[->, thick, shorten >=15pt] (L2.east) to [out=0, in=180] (R4.west);
    \draw[->, thick, shorten >=15pt] (L3.east) to [out=0, in=180] (R3.west);
\end{tikzpicture}

\vspace{1.5em}\pause

\textbf{Gaps in Literature:}
\vspace{2mm}
\begin{enumerate}
    \item Findings are limited to large, publicly traded firms
    \item Unclear in the context of exogenous policy shocks
\end{enumerate}

@@

@@

\vspace{10mm} \large

\begin{enumerate}
    \item Nonprofits drive the hospital industry \scriptsize (\cite{ASPE_2023}) \large

    \item Policies often aim to improve the value of health care delivery

@@

@@

\begin{frame}{Research Question}
    \centering
    \Large
    Does having clinically trained executives

@@

    affect the response to pay-for-performance incentives

@@

\begin{frame}{More Details}
    \large
    I leverage several 2012 pay-for-performance initiatives

    \vspace{2mm}
    \begin{wideitemize}
        \item Penalty (reward) for below (above) average \hspace{-8mm} $\underbrace{\text{quality}}_{\text{30-day read \& mort}}$
        \item \textit{Changes the relationship between revenue and quality in objective function}
    \end{wideitemize}

    Why clinical training?

    \vspace{2mm}
    \begin{wideitemize}
        \item Potentially correlated with hospital's preferences towards revenue versus patient welfare
    \end{wideitemize}

\begin{frame}{Final Data Set}

@@

    \textbf{Executives:}

    \begin{itemize}
        \item Top level C-suite employees scraped from 990s
    \end{itemize}

    \textbf{Hospital:}

    \vspace{1mm}
    \begin{wideitemize}
        \item AHA, Hospital Compare, CMS Case Mix Index, HCRIS
    \end{wideitemize}

@@

    \begin{itemize}
        \item Manually match physician executives to NPPES NPI number
    \end{itemize}

    \textbf{Years: 2010-2014}
\end{frame}

@@

\begin{frame}{Executive Teams}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
\toprule
 & Ever & Always & Never\\
  & Clinical Exec & Clinical Exec & Clinical Exec\\
\midrule
\addlinespace[0.3em]
Number Executives & 4.82 & 5.19 & 2.86\\
Fraction Clinical Execs & 0.20 & 0.26 & 0.00\\
Has a CMO & 0.55 & 0.52 & 0.07\\
Has Clinical CEO & 0.25 & 0.10 & 0.00\\
\addlinespace[0.6em]
Num. Hospitals & 452 & 62 & 385\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@

@@

    Different methods:
    \begin{itemize}
        \item No weights
        \item \textbf{Weights based on outcomes pre-2012} 
        \item Coarsened exact matching 
    \end{itemize}
\end{frame}

\begin{frame}{Identification Assumptions}\label{ident}

\large
\begin{wideitemize}
    \item Parallel trends
    \item No other 2012 event correlated with executive team and outcomes
    \item No hospital characteristics perfectly correlated with executive team
    \item Stability in clinical executives not correlated with incentive change \hyperlink{changes}{\beamergotobutton{analysis}}
    \begin{itemize}
        \item No correlation between 2012 and likelihood of changing propensity to hire clinical executive
        \item No correlation between exposure to policies and likelihood of changing propensity
    \end{itemize}
\end{wideitemize}
\end{frame}

@@

\begin{frame}{Estimation}
\large
    \textbf{Compare both nonprofit leadership team types to for-profits:}

@@

    Comparison groups:
    \begin{itemize}
        \item nonprofit clinical; nonprofit non-clinical
    \end{itemize}

@@

\begin{frame}{Mortality Rate}\label{forprofmort}
    \begin{columns}
    \column{0.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_md_synth_graph.pdf}
    \column{0.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_nomd_synth_graph.pdf}
    \end{columns}

    \hyperlink{unobserved}{\beamergotobutton{unobserved}}
\end{frame}

\section{Unobserved}

@@

@@

    \textbf{Implications}

    \vspace{2mm}
    \begin{wideitemize}
        \item Despite all being nonprofits, hospitals with clinician leaders act more like we would expect nonprofits to
        \item In the absence of clinical leadership, nonprofits just act like for-profits
    \end{wideitemize}

@@

    \begin{center}
        \Large Thank you! 
    \end{center}
\end{frame}

@@

\begin{wideitemize}
    \item Care transition from inpatient to outpatient
    \item Patient education
    \item Improve care coordination
    \item Follow-up appointments
\end{wideitemize}

@@

\begin{frame}{Hospital Statistics}\label{sumstats}
\vspace{-3mm}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
 & Ever & Always & Never\\
  & Clinical Exec &Clinical Exec &Clinical Exec\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
\hspace{1em}Academic Med. Center & 0.41 & 0.51 & 0.20\\
\hspace{1em}Number Beds & 227 & 218 & 102\\
\hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
\hspace{1em}System Affiliated & 0.57 & 0.56 & 0.42\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
\hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.77 & 0.59\\
\hspace{1em}Penalized for one condition & 0.19 & 0.25 & 0.13\\
\hspace{1em}Penalized for two conditions & 0.50 & 0.47 & 0.38\\
\hspace{1em}Penalized for all Conditions & 0.31 & 0.31 & 0.20\\
\bottomrule
\end{tabular}
\end{table}
\hyperlink{forprofitstats}{\beamergotobutton{for-profit stats}}
\end{frame}

@@

\begin{frame}{Raw Outcomes with For-Profit}\label{fp_outcomes}
\begin{center}
    \includegraphics[width=\textwidth]{Objects/outcomes_graph_fp.pdf}
\end{center}
    \btVFill
    \hyperlink{outcomes}{\beamerreturnbutton{outcomes graph}}
\end{frame}

@@

\begin{frame}{Results by Specialty}\label{specialty}
\begin{center}
    \includegraphics[width=.4\textwidth]{Objects/read_nospecialty_nomd_synth_graph.pdf}
\end{center}

\begin{frame}{Average Team Changes Over Time}\label{changes}
\centering 
    \includegraphics[width=.8\textwidth]{Objects/change_means.pdf}
\end{frame}

    \hyperlink{ident}{\beamerreturnbutton{back}}

\begin{frame}{Driven by Unobserved Compositional Differences?}\label{unobserved}
\large

\textbf{Concern:} presence of clinicians may not matter but is correlated with some unobserved hospital `type', possibly time varying

\vspace{3mm}
\begin{wideitemize}
    \item if true, we should see a difference in response no matter the timing of having a clinical executive
\end{wideitemize}
\end{frame}

\begin{frame}{Robustness Check}
\large
    \begin{figure}[ht!]
\begin{center}

 \begin{tabular}{| m{15em} |}
 \hline \vspace{1mm}
 \textbf{Signaling Effect:}\\ [0.5ex]
 \hline\hline 
 \vspace{2mm}
 Treat Group:  \hspace{15mm} Never MD \\
 \vspace{2mm}
 Comparison Group: \hspace{3mm} Ever MD  \\
 [1ex]
 \hline
 \end{tabular}
\hfil   %<---
 \begin{tabular}{|m{18em}|}
 \hline \vspace{1mm}
 \textbf{Clinician Effect:}\\ [0.5ex]
 \hline\hline
 \vspace{2mm}
 Treat Group: \hspace{11mm} MD in 2012 \\
 \vspace{2mm}
 Comparison Group:  MD not in 2012  \\
 [1ex]
 \hline
 \end{tabular}

\begin{frame}{Results}
    \begin{table}[ht!]
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\underline{Weighted Avg. Readmission Rate}} & \multicolumn{2}{c}{\underline{Weighted Avg. Mortality Rate}} \\
 & (1) & (2) & (3) & (4)\\
\midrule
Signaling Effect & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
Clinician Effect &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
Observations & 3,005 & 1,595 & 3,005 & 1,595\\
\bottomrule
\end{tabular}
\end{table}

\hyperlink{forprofmort}{\beamerreturnbutton{back}}
\end{frame}
